\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{green}
\usepackage[scale=0.75]{geometry}

\firstname{Alex}
\familyname{Chesters}
\title{Curriculum Vitae}
\email{alex@cheste.rs}
\homepage{cheste.rs}

\begin{document}
\makecvtitle

\section{Experience}
\cventry{August 2019 - Present}{Senior Software Engineer}{British Broadcasting Corporation}{}{}{In August 2019 I was promoted to my current position of Senior Software Engineer. Whilst continuing to work on the development of the BBC's Connected TV applications, I now also lead the Continuous Delivery Guild; a cross-discipline community exploring the obstacles to Continuous Delivery in BBC iPlayer \& Sounds.}
\cventry{September 2017 - August 2019}{Software Engineer}{British Broadcasting Corporation}{}{}{In September 2017 I was promoted to the role of Software Engineer, continuing to work in the division now known as BBC Design \& Engineering on the BBC's Connected TV applications.}
\cventry{January 2017 - September 2017}{Junior Software Engineer}{British Broadcasting Corporation}{}{}{In January 2017 I completed my apprenticeship scheme and began the role of a Junior Software Engineer; I continued to work in the division now known as BBC Design \& Engineering on the BBC's various Connected TV applications.}
\cventry{September 2014 - January 2017}{Apprentice Software Engineer}{British Broadcasting Corporation}{}{}{Between September 2014 and January 2017 I worked as an Apprentice Software Engineer at the BBC whilst completing a Level 4 Higher Apprenticeship in IT, Software and Web at The Manchester College. I worked in the division now known as BBC Design \& Engineering MediaCityUK, developing applications including BBC iPlayer, Sport, News and Red Button+ for Connected TV devices, such as smart TVs, set-top boxes and games consoles.}

\section{Licenses and Certifications}
\cventry{}{Mental Health First Aider}{MHFA England}{}{}{I am a Mental Health First Aider, qualified in providing first aid to people who may be experiencing mental health issues such as depression, anxiety and psychosis.}
\cventry{}{AWS Certificated Solutions Architect - Associate}{Amazon Web Services}{}{}{I am a Mental Health First Aider, qualified in providing first aid to people who may be experiencing mental health issues such as depression, anxiety and psychosis.}

\section{Accomplishments}
\cventry{2016}{Apprentice of the Year}{BBC Design \& Engineering}{}{}{}

\section{Education}
\cventry{September 2014 - May 2016}{The Manchester College}{}{Manchester}{}{Level 4 Higher Apprenticeship in IT, Software and Web}
\cventry{September 2012 - May 2014}{Barrow Hall College}{}{Warrington}{}{Attained four AS Levels in Media, Applied ICT, Law and Economics and three A2 levels in Applied ICT, Law and Economics.}
\cventry{September 2007 - May 2012}{Great Sankey High School}{}{Warrington}{}{Attained 9 GCSEs.}

\end{document}
